Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-06 paper/structureScene.tex
moving to monochrome. Sad but true.

\subsection{Gammatone wavelets}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gammatones}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
\end{center}
\end{figure}
Wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as fourth-order Gammatone
wavelets with one vanishing moment \cite{Venkitaraman2014}, and are shown in Figure \ref{fig:gammatones}.
In the context of auditory scene analysis, the asymmetric envelope of Gammatone wavelets is more biologically plausible than the symmetric, Gaussian-like envelope of the more widely used Morlet wavelets.
Indeed, it allows to reproduce two important psychoacoustic effects in the mammalian cochlea: the asymmetry of temporal masking and the asymmetry of spectral masking  \cite{Fastl2007}.
Moreover, it should be noted that Gammatone wavelets follow the typical amplitude profile of natural sounds, beginning with a relatively sharp attack and ending with a slower decay.
As such, they can be discovered automatically by unsupervised encoding of natural sounds \cite{Smith2006}.
This suggests that, despite being hand-crafted and not learned, Gammatone wavelets provide a sparse time-frequency representation of acoustic scenes.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{compression}
\caption{
\label{fig:histograms}
Histogram of values taken by the first-order scattering coefficient $\mathbf{S}\boldsymbol{x}(\gamma)$, corresponding to a center acoustic frequency of $302\,\mathrm{Hz}$,
(a) before and (b) after logarithmic compression.}
\label{fig:compression}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{gfx/unsupervised_test2}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_1}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{gfx/unsupervised_test1}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering coefficients, with and without logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}}
\end{center}
\label{fig:folds}
\end{figure}

>>>>

\subsection{Gammatone wavelets}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{bw/gammatones}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. 
\vl{If you want to keep this level of detail you have to adapt the figure so that it is readable in greyscale. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
}
\end{center}
\end{figure}
Wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as fourth-order Gammatone
wavelets with one vanishing moment \cite{Venkitaraman2014}, and are shown in Figure \ref{fig:gammatones}.
In the context of auditory scene analysis, the asymmetric envelope of Gammatone wavelets is more biologically plausible than the symmetric, Gaussian-like envelope of the more widely used Morlet wavelets.
Indeed, it allows to reproduce two important psychoacoustic effects in the mammalian cochlea: the asymmetry of temporal masking and the asymmetry of spectral masking  \cite{Fastl2007}.
Moreover, it should be noted that Gammatone wavelets follow the typical amplitude profile of natural sounds, beginning with a relatively sharp attack and ending with a slower decay.
As such, they can be discovered automatically by unsupervised encoding of natural sounds \cite{Smith2006}.
This suggests that, despite being hand-crafted and not learned, Gammatone wavelets provide a sparse time-frequency representation of acoustic scenes.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{bw/compression}
\caption{
\label{fig:histograms}
Histogram of values taken by the first-order scattering coefficient $\mathbf{S}\boldsymbol{x}(\gamma)$, corresponding to a center acoustic frequency of $302\,\mathrm{Hz}$,
(a) before and (b) after logarithmic compression.}
\label{fig:compression}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{bw/unsupervised_test2}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for MFCCs and scattering with logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_1}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{bw/unsupervised_test1}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering coefficients, with and without logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{bw/folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies.  Performance on each fold is depicted using a given symbol.
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.}
\end{center}
\label{fig:folds}
\end{figure}
